---
title: "Shedding new light on ovulatory cycle shifts in women’s mate attraction and preferences"
author: "Julia Stern"
date: "May 2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error=TRUE)
knitr::opts_chunk$set(warning=FALSE)
```


```{r load packages}
library(tidyverse)
library(lme4)
library(lmerTest)
library(knitr)
library(psych)
library(dplyr)
library(GPArotation)
library(sjPlot)
library(sjmisc)
```

##Load raw Data
Data from N = 257 heterosexual, naturally cycling women. Each row is the data from a single session.
See variable names below:

```{r raw data}
setwd("C:/Users/jjuenge/Desktop/data")
#rating raw data
data_raw <- read.csv("cycle2_rating_male_bodies.csv",sep =";",dec =",", header=TRUE)

#numbers as numeric, factors as factor
for(i in c(2,4:9, 11:52)){
  data_raw[,i] <- as.numeric(as.character(data_raw[,i]))
}

for(i in c(1,3,10)){
  data_raw[,i] <- as.factor(unlist(data_raw[,i]))
}

#male body measures
male_bodies <- read.csv("male_body_characteristics_full.csv",sep =";",dec =",", header=TRUE)

for(i in c(2:14)){
  male_bodies[,i] <- as.numeric(as.character(male_bodies[,i]))
}


```


##Load cleaned combined long-format data
#Please check the OSF (https://osf.io/4jcuf/) for description of variables and their names

```{r load data}
#this dataset is used for all analyses!

setwd("C:/Users/jjuenge/Desktop/data")
#data <-read.csv("data_cycle2_malebodies_cleaned.csv",sep =";",dec =",", header=TRUE)
data <-read.csv("data_male_female_bodies_objects.csv",sep =";",dec =",", header=TRUE)

##numbers as numeric, categories as factor variables
for(i in c(3,5:9,11:26,28, 29,31)){
  data[,i] <- as.numeric(as.character(data[,i]))
}

for(i in c(1,2,4,10,27,30)){
  data[,i] <- as.factor(data[,i])
}


#Scale sexual desire, self-reported stress and all male variables
data$roney_desire <- scale(data$roney_desire)
data$stress <- scale(data$stress)
data$strength <- scale(data$strength)
data$height <- scale(data$height)
data$upperarmgirth_mean_leftright <- scale(data$upperarmgirth_mean_leftright)
data$SHR <- scale(data$SHR)
data$SCR <- scale(data$SCR)
data$rel_torso_vol <- scale(data$rel_torso_vol)
data$testosterone_men <- scale(data$testosterone_men)
data$dominance <- scale(data$dominance)
data$Muscularity <- scale(data$Muscularity)
data$BMI <- scale(data$BMI)
data$WHtR <- scale(data$WHtR)
data$WHR <- scale(data$WHR)
data$Male_Age <- scale(data$Male_Age)

```

#Add mean hormone levels for between-women hormone analyses
#And subject-mean-centred the hormone values for within-women analyses
```{r Subject-mean-centre hormones}


#############################################################################################################
#add between-women values

#for mean non-transformed hormone values
data<-data%>% group_by(Person) %>% mutate(estradiol_mean = mean(estradiol, na.rm=TRUE), 
                                              progesterone_mean = mean(progesterone, na.rm=TRUE),
                                              E_P_mean = mean(E_P, na.rm=TRUE))


#Scale untransformed mean hormones
data$estradiol_mean <- scale(data$estradiol_mean)
data$progesterone_mean <- scale(data$progesterone_mean)
data$E_P_mean <- scale(data$E_P_mean)


#subject-mean-centre hormones
# and divide by a constant to put all hormones on ~ -0.5 to +0.5 scale

data <- data %>%
  group_by(Person) %>%
  mutate(progesterone = (progesterone - mean(progesterone, na.rm=TRUE))/90,
         estradiol = (estradiol - mean(estradiol, na.rm=TRUE))/4,
         E_P = (E_P-mean(E_P, na.rm=TRUE))/3) %>%
  ungroup() %>%
  as.data.frame()
data %>%
  group_by(Person, progesterone,estradiol, E_P) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  gather("hormone", "value", progesterone:E_P) %>%
  ggplot(aes(value, colour=hormone)) +
  geom_density(alpha=.5) +
  scale_x_continuous(limits = c(-1,1))

```
#Factor analysis for body measures and correlation matrix
```{r factor analysis}
names(male_bodies)

male_bodies$strength <- scale(male_bodies$strength)
male_bodies$height <- scale(male_bodies$height)
male_bodies$upperarmgirth_mean_leftright <- scale(male_bodies$upperarmgirth_mean_leftright)
male_bodies$SHR <- scale(male_bodies$SHR)
male_bodies$SCR <- scale(male_bodies$SCR)
male_bodies$rel_torso_vol <- scale(male_bodies$rel_torso_vol)
male_bodies$testosterone_men <- scale(male_bodies$testosterone_men)
male_bodies$dominance <- scale(male_bodies$dominance)
male_bodies$Muscularity <- scale(male_bodies$Muscularity)
male_bodies$BMI <- scale(male_bodies$BMI)
male_bodies$WHtR <- scale(male_bodies$WHtR)
male_bodies$WHR <- scale(male_bodies$WHR)
male_bodies$Age <- scale(male_bodies$Age)


measures <- male_bodies[,c("strength","height","upperarmgirth_mean_leftright", "SHR", "SCR", "rel_torso_vol","testosterone_men")]

#correlation matrix
cor(measures)
?fa.parallel

#How many factors for exploratory factor analysis?
parallel <- fa.parallel(measures, fm = 'ml', fa = 'fa')

#test revealed 2 factors.
EFA <- fa(measures, nfactors = 2, fm="ml", rotate="oblimin", scores = "regression", use="complete.obs", max.iter=50)

#Show factor loadings (Table S9)
loadings(EFA)
print.psych(EFA, cut=0.3, sort=T)

#Save new factors, rename them and and merge to data and data2
EFA <- as.data.frame(cbind(EFA$scores))
measures2 <- cbind(male_bodies$MaleID, EFA)
colnames(measures2) <- c("MaleID","shoulder_factor", "strength_factor")
data <- merge(data, measures2, by = "MaleID")

cor.test(measures2$shoulder_factor, measures2$strength_factor)

table(data$conception_risk)

```
###Analyses

#Cycle shifts in attractiveness ratings: Attraction

```{r Cycle shifts in attraction}

###Are there cycle shifts in women's attraction?

#Hypothesis 1a
model1a <- lmer(Rating ~ conception_risk + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk||Person), data = data)
tab_model(model1a, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#with E_P ratio, Hypothesis 1b
model1b <- lmer(Rating ~ E_P + ( 1 | Person) + (1 | MaleID) + (1 + E_P||Person), data = data)
tab_model(model1b, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#moderated by relationship status, Hypothesis 1c
#Table 1
model1c<- lmer(Rating ~ conception_risk * relationship_status + (1 |Person) + (1 | MaleID) + (1+ conception_risk*relationship_status||Person),  data = data)
tab_model(model1c, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#moderated by relationship status, but with E_P ratio, Hypothesis 1d
#Table 1
model1c2<- lmer(Rating ~ E_P * relationship_status + (1 |Person) + (1 | MaleID) + (1+ E_P*relationship_status||Person),  data = data)
tab_model(model1c2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)


#moderated by self-reported stress, Hypothesis 1d
#Table S4
model1d<- lmer(Rating ~ conception_risk * stress + (1 |Person) + (1 | MaleID) + (1+ conception_risk*stress||Person),  data = data)
tab_model(model1d, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#moderated by self-reported stress, but with E_P ratio, Hypothesis 1d
#Table S4
model1d2<- lmer(Rating ~ E_P * stress + (1 |Person) + (1 | MaleID) + (1+ E_P*stress||Person),  data = data)
tab_model(model1d2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#shifts in mate attraction mediated by sexual desire? H1e


#Premises H1e:
#effect of mediator on outcome
model_p1_H1e1 <- lmer(Rating ~ roney_desire + ( 1 | Person) + (1 | MaleID) + (1 + roney_desire||Person), data = data)
tab_model(model_p1_H1e1, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#effect of predictor on mediator
model_p2_H1e1 <- lmer(roney_desire ~ conception_risk + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk||Person), data = data)
tab_model(model_p2_H1e1, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Test H1e:
modelH1e1<- lmer(Rating ~ conception_risk +roney_desire + (1 | Person) + (1 | MaleID) + (1 + conception_risk + roney_desire || Person), data = data)
tab_model(modelH1e1, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for E/P rather than conception risk
#premise: Effect of predictor on mediator
P2_modelH1e2<- lmer(roney_desire ~ E_P + (1 | Person) + (1 | MaleID) + (1+ E_P||Person), data = data)
tab_model(P2_modelH1e2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#testing Hypothesis 1e for E/P
modelH1e2<- lmer(Rating ~ E_P + roney_desire + (1 | Person) + (1 | MaleID) + (1 + E_P + roney_desire||Person), data = data)
tab_model(modelH1e2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 1f: Attraction shift (of conception risk) mediated by E/P?

#Premise H1f:
P_modelH1f<- lmer(E_P ~ conception_risk + (1 | Person) + (1 | MaleID) + (1+conception_risk||Person), data = data)
tab_model(P_modelH1f,show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Test H1f:
modelH1f<- lmer(Rating ~ conception_risk + E_P + (1 | Person) + (1 | MaleID) + (1+conception_risk+ E_P||Person), data = data)
tab_model(modelH1f,show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

```



##Exploratory analyses: Attraction shifts
```{r}
#repeat the analyses above with estradiol and progesterone separately rather than E/P

#names(data)

#main effect of estradiol and progesterone on men's attractiveness rating, Table S5
model_e1 <- lmer(Rating ~ estradiol + progesterone + ( 1 | Person) + (1 | MaleID) + (1 + estradiol + progesterone||Person), data = data)
tab_model(model_e1, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
summary(model_e1)


#moderated by relationship status, Table S6
model_e2 <- lmer(Rating ~ estradiol*relationship_status + progesterone*relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + estradiol*relationship_status + progesterone*relationship_status||Person), data = data)
tab_model(model_e2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
summary(model_e2)


#moderated by self-reported stress, Table S7
model_e3 <- lmer(Rating ~ estradiol*stress + progesterone*stress + ( 1 | Person) + (1 | MaleID) + (1 + estradiol*stress + progesterone*stress||Person), data = data)
tab_model(model_e3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
summary(model_e3)

#shifts in mate attraction mediated by sexual desire? H1e

#premise: Effect of predictors on mediator Table S8
model_e4 <- lmer(roney_desire ~ estradiol + progesterone + ( 1 | Person) + (1 | MaleID) + (1 + estradiol + progesterone||Person), data = data)
tab_model(model_e4, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
summary(model_e4)


#testing Hypothesis 1e with estradiol and progesterone separately Table S9
model_e5 <- lmer(Rating ~ estradiol + progesterone + roney_desire + ( 1 | Person) + (1 | MaleID) + (1 + estradiol + progesterone + roney_desire||Person), data = data)
tab_model(model_e5, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
summary(model_e5)


#Hypothesis 1f: Attraction shift (of conception risk) mediated by estradiol or progesterone

#Premise H1f Table S10
model_e6 <- lmer(conception_risk ~ estradiol + progesterone + ( 1 | Person) + (1 | MaleID) + (1 + estradiol + progesterone||Person), data = data)
tab_model(model_e6, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)


#Test H1f Table S11
model_e7 <- lmer(Rating ~ estradiol + progesterone + conception_risk + ( 1 | Person) + (1 | MaleID) + (1 + estradiol + progesterone + conception_risk||Person), data = data)
tab_model(model_e7, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

```
```{r attraction for womens bodies}
###Are there cycle shifts in women's attraction to other women?

#Hypothesis 1a
f_model1a <- lmer(Rating_f ~ conception_risk + ( 1 | Person) + (1 | FemaleID) + (1 + conception_risk||Person), data = data)
tab_model(f_model1a, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#with E_P ratio, Hypothesis 1b
#Table S12
f_model1b <- lmer(Rating_f ~ E_P + ( 1 | Person) + (1 | FemaleID) + (1 + E_P||Person), data = data)
tab_model(f_model1b, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#moderated by relationship status, Hypothesis 1c
#Table S13
f_model1c<- lmer(Rating_f ~ conception_risk * relationship_status + (1 |Person) + (1 | FemaleID) + (1+ conception_risk*relationship_status||Person),  data = data)
tab_model(f_model1c, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#moderated by relationship status, but with E_P ratio, Hypothesis 1d
#Table S14
f_model1c2<- lmer(Rating_f ~ E_P * relationship_status + (1 |Person) + (1 | FemaleID) + (1+ E_P*relationship_status||Person),  data = data)
tab_model(f_model1c2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)


#moderated by self-reported stress, Hypothesis 1d
#Table S15
f_model1d<- lmer(Rating_f ~ conception_risk * stress + (1 |Person) + (1 | FemaleID) + (1+ conception_risk*stress||Person),  data = data)
tab_model(f_model1d, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#moderated by self-reported stress, but with E_P ratio, Hypothesis 1d
#Table S16
f_model1d2<- lmer(Rating_f ~ E_P * stress + (1 |Person) + (1 | FemaleID) + (1+ E_P*stress||Person),  data = data)
tab_model(f_model1d2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#shifts in mate attraction mediated by sexual desire? H1e


#Premises H1e:
#effect of mediator on outcome
f_model_p1_H1e1 <- lmer(Rating_f ~ roney_desire + ( 1 | Person) + (1 | FemaleID) + (1 + roney_desire||Person), data = data)
tab_model(f_model_p1_H1e1, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)


#Test H1e:
#Table S17
f_modelH1e1<- lmer(Rating_f ~ conception_risk +roney_desire + (1 | Person) + (1 | FemaleID) + (1 + conception_risk + roney_desire || Person), data = data)
tab_model(f_modelH1e1, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)


#Preference shift for female muscularity?

#Hypothesis 2a: for muscularity
#Table S18
f_model2a <- lmer(Rating_f ~ conception_risk * Muscularity_f + ( 1 | Person) + (1 | FemaleID) + (1 + conception_risk * Muscularity_f||Person), data = data)
tab_model(f_model2a, show.std = TRUE,show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
```


```{r attraction for objects}
###Are there cycle shifts in women's attraction to objects (control)?

#Hypothesis 1a
o_model1a <- lmer(Rating_o ~ conception_risk + ( 1 | Person) + (1 | ObjectID) + (1 + conception_risk||Person), data = data)
tab_model(o_model1a, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#with E_P ratio, Hypothesis 1b
#Table S12
o_model1b <- lmer(Rating_o ~ E_P + ( 1 | Person) + (1 | ObjectID) + (1 + E_P||Person), data = data)
tab_model(o_model1b, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#moderated by relationship status, Hypothesis 1c
#Table S13
o_model1c<- lmer(Rating_o ~ conception_risk * relationship_status + (1 |Person) + (1 | ObjectID) + (1+ conception_risk*relationship_status||Person),  data = data)
tab_model(o_model1c, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#moderated by relationship status, but with E_P ratio, Hypothesis 1d
#Table S14
o_model1c2<- lmer(Rating_o ~ E_P * relationship_status + (1 |Person) + (1 | ObjectID) + (1+ E_P*relationship_status||Person),  data = data)
tab_model(o_model1c2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)


#moderated by self-reported stress, Hypothesis 1d
#Table S15
o_model1d<- lmer(Rating_o ~ conception_risk * stress + (1 |Person) + (1 | ObjectID) + (1+ conception_risk*stress||Person),  data = data)
tab_model(o_model1d, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#moderated by self-reported stress, but with E_P ratio, Hypothesis 1d
#Table S16
o_model1d2<- lmer(Rating_o ~ E_P * stress + (1 |Person) + (1 | ObjectID) + (1+ E_P*stress||Person),  data = data)
tab_model(o_model1d2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#shifts in object attraction mediated by sexual desire? H1e

#Test H1e:
#Table S17
o_modelH1e1<- lmer(Rating_o ~ conception_risk +roney_desire + (1 | Person) + (1 | ObjectID) + (1 + conception_risk + roney_desire || Person), data = data)
tab_model(o_modelH1e1, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

```

#Cycle shifts in attractiveness ratings: Mate preferences
#Hypotheses Block 2

```{r mate preference shifts}

#add between-women hormone effects

#Hypothesis 2a: for muscularity
#Table 2
model2a <- lmer(Rating ~ conception_risk * Muscularity + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk * Muscularity||Person), data = data)
tab_model(model2a,show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2b: for dominance
#Table 2
model2b <- lmer(Rating ~ conception_risk * dominance + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance||Person), data = data)
tab_model(model2b, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2c: for factor 1
#Table 2
model2c <- lmer(Rating ~ conception_risk * shoulder_factor + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor||Person), data = data)
tab_model(model2c, show.std = TRUE, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2c: for factor 2
#Table 2
model2c2 <- lmer(Rating ~ conception_risk * strength_factor + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor||Person), data = data)
tab_model(model2c2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#######################################################################################################
#with E/P rather than conception risk, Hypothesis 2f, Table 4
#also including between-women hormone effects in an exploratory manner

#for muscularity
#Table 3
model2f1 <- lmer(Rating ~ E_P * Muscularity + E_P_mean * Muscularity + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity ||Person), data = data)
#tab_model(model2f1, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
summary(model2f1)

#for dominance
#Table 3
model2f2 <- lmer(Rating ~ E_P * dominance + E_P_mean* dominance + ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance||Person), data = data)
#tab_model(model2f2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
summary(model2f2)

#for factor 1
#Table 3
model2f3 <- lmer(Rating ~ E_P * shoulder_factor + E_P_mean* shoulder_factor + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor||Person), data = data)
#tab_model(model2f3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
summary(model2f3)

#for factor 2
#Table 3
model2f4 <- lmer(Rating ~ E_P * strength_factor + E_P_mean*strength_factor + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor||Person), data = data)
#tab_model(model2f4, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
summary(model2f4)

########################################################################################################

#3-way Interactions with relationship status: Hypothesis 2d
#for muscularity
#Table S24
model2d <- lmer(Rating ~ conception_risk * Muscularity * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity*relationship_status||Person), data = data)
tab_model(model2d, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S24
model2d2 <- lmer(Rating ~ conception_risk * dominance*relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance*relationship_status||Person), data = data)
tab_model(model2d2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for shoulder factor #Table S25
model2d3 <- lmer(Rating ~ conception_risk * shoulder_factor*relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor*relationship_status||Person), data = data)
tab_model(model2d3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for strength factor #Table S25
model2d4 <- lmer(Rating ~ conception_risk * strength_factor*relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor*relationship_status||Person), data = data)
tab_model(model2d4, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################
#with E/P rather than  conception risk

#also including between-women hormone effects in an exploratory manner

#for muscularity #Table S26
model2d5 <- lmer(Rating ~ E_P * Muscularity*relationship_status + E_P_mean * Muscularity*relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity*relationship_status ||Person), data = data)
tab_model(model2d5, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S27
model2d6 <- lmer(Rating ~ E_P * dominance*relationship_status + E_P_mean* dominance*relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance*relationship_status||Person), data = data)
tab_model(model2d6, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1 #Table S28
model2d7 <- lmer(Rating ~ E_P * shoulder_factor*relationship_status + E_P_mean* shoulder_factor*relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor* relationship_status||Person), data = data)
tab_model(model2d7, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2 #Table S29
model2d8 <- lmer(Rating ~ E_P * strength_factor*relationship_status + E_P_mean*strength_factor*relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor*relationship_status||Person), data = data)
tab_model(model2d8, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
```

```{r self reported stress}
########################################################################################################

#3-way Interactions with self-reported stress: Hypothesis 2e
#for muscularity #Table S30
model2e <- lmer(Rating ~ conception_risk * Muscularity * stress + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity*stress||Person), data = data)
tab_model(model2e, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S30
model2e2 <- lmer(Rating ~ conception_risk * dominance*stress + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance*stress||Person), data = data)
tab_model(model2e2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for shoulder factor #Table S31
model2e3 <- lmer(Rating ~ conception_risk * shoulder_factor*stress + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor*stress||Person), data = data)
tab_model(model2e3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for strength factor #Table S31
model2e4 <- lmer(Rating ~ conception_risk * strength_factor*stress + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor*stress||Person), data = data)
tab_model(model2e4, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################
#with E/P rather than  conception risk

#also including between-women hormone effects in an exploratory manner

#for muscularity #Table S32
model2e5 <- lmer(Rating ~ E_P * Muscularity*stress + E_P_mean * Muscularity*stress + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity*stress ||Person), data = data)
tab_model(model2e5, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S33
model2e6 <- lmer(Rating ~ E_P * dominance*stress + E_P_mean* dominance*stress + ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance*stress||Person), data = data)
tab_model(model2e6, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1 #Table S34
model2e7 <- lmer(Rating ~ E_P * shoulder_factor*stress + E_P_mean* shoulder_factor*stress + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor*stress||Person), data = data)
tab_model(model2e7, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2 #Table S35
model2e8 <- lmer(Rating ~ E_P * strength_factor*stress + E_P_mean*strength_factor*stress + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor*stress||Person), data = data)
tab_model(model2e8, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

```

```{r WHtR body fat mass}
#controlling for body fat mass (with WHtR), Hypothesis 2g

#Hypothesis 2a controlling for WHtR #Table S36
model2g_fat <- lmer(Rating ~ conception_risk * Muscularity + WHtR * Muscularity+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity + WHtR * Muscularity||Person), data = data)
tab_model(model2g_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2b: for dominance #Table S36
model2b_fat <- lmer(Rating ~ conception_risk * dominance + WHtR *dominance + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance + WHtR *dominance||Person), data = data)
tab_model(model2b_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2c: for factor 1 #Table S37
model2c_fat <- lmer(Rating ~ conception_risk * shoulder_factor + WHtR *shoulder_factor + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor + WHtR *shoulder_factor||Person), data = data)
tab_model(model2c_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2c: for factor 2 #Table S37
model2c2_fat <- lmer(Rating ~ conception_risk * strength_factor + WHtR *strength_factor + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor + WHtR *strength_factor||Person), data = data)
tab_model(model2c2_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#######################################################################################################
#with E/P rather than conception risk, Hypothesis 2f, Table 4
#also including between-women hormone effects in an exploratory manner

#for muscularity #Table S38
model2f1_fat <- lmer(Rating ~ E_P * Muscularity + E_P_mean * Muscularity + WHtR *Muscularity + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity + WHtR *Muscularity ||Person), data = data)
tab_model(model2f1_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S38
model2f2_fat <- lmer(Rating ~ E_P * dominance + E_P_mean* dominance + WHtR *dominance + ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance + WHtR *dominance||Person), data = data)
tab_model(model2f2_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1 #Table S39
model2f3_fat <- lmer(Rating ~ E_P * shoulder_factor + E_P_mean* shoulder_factor + WHtR *shoulder_factor + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor+ WHtR *shoulder_factor||Person), data = data)
tab_model(model2f3_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2 #Table S39
model2f4_fat <- lmer(Rating ~ E_P * strength_factor + E_P_mean*strength_factor + WHtR *strength_factor + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor + WHtR *strength_factor||Person), data = data)
tab_model(model2f4_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################

#3-way Interactions with relationship status: Hypothesis 2d
#for muscularity #Table S40
model2d_fat <- lmer(Rating ~ conception_risk * Muscularity * relationship_status + WHtR *Muscularity* relationship_status+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity*relationship_status + WHtR *Muscularity*relationship_status||Person), data = data)
tab_model(model2d_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S41
model2d2_fat <- lmer(Rating ~ conception_risk * dominance*relationship_status + WHtR *dominance*relationship_status+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance*relationship_status + WHtR *dominance *relationship_status||Person), data = data)
tab_model(model2d2_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for shoulder factor #Table S42
model2d3_fat <- lmer(Rating ~ conception_risk * shoulder_factor*relationship_status + WHtR *shoulder_factor * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor*relationship_status + WHtR *shoulder_factor* relationship_status||Person), data = data)
tab_model(model2d3_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for strength factor #Table S43
model2d4_fat <- lmer(Rating ~ conception_risk * strength_factor*relationship_status + WHtR *strength_factor * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor*relationship_status + WHtR *strength_factor * relationship_status||Person), data = data)
tab_model(model2d4_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################
#with E/P rather than  conception risk

#also including between-women hormone effects in an exploratory manner

#for muscularity #Table S44
model2d5_fat <- lmer(Rating ~ E_P * Muscularity*relationship_status + E_P_mean * Muscularity*relationship_status + WHtR *Muscularity * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity*relationship_status + WHtR *Muscularity * relationship_status||Person), data = data)
tab_model(model2d5_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S45
model2d6_fat <- lmer(Rating ~ E_P * dominance*relationship_status + E_P_mean* dominance*relationship_status + WHtR * dominance * relationship_status+ ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance*relationship_status + WHtR *dominance * relationship_status||Person), data = data)
tab_model(model2d6_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1 #Table S46
model2d7_fat <- lmer(Rating ~ E_P * shoulder_factor*relationship_status + E_P_mean* shoulder_factor*relationship_status + WHtR *shoulder_factor * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor* relationship_status + WHtR *shoulder_factor* relationship_status||Person), data = data)
tab_model(model2d7_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2 #Table S47
model2d8_fat <- lmer(Rating ~ E_P * strength_factor*relationship_status + E_P_mean*strength_factor*relationship_status + WHtR * strength_factor * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor*relationship_status + WHtR *strength_factor * relationship_status||Person), data = data)
tab_model(model2d8_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#3-way Interactions with self-reported stress: Hypothesis 2e
#for muscularity #Table S48
model2e_fat <- lmer(Rating ~ conception_risk * Muscularity * stress + WHtR * Muscularity * stress+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity*stress + WHtR *Muscularity * stress||Person), data = data)
tab_model(model2e_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S49
model2e2_fat <- lmer(Rating ~ conception_risk * dominance*stress + WHtR * dominance * stress+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance*stress + WHtR *dominance * stress||Person), data = data)
tab_model(model2e2_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for shoulder factor #Table S50
model2e3_fat <- lmer(Rating ~ conception_risk * shoulder_factor*stress + WHtR * shoulder_factor * stress + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor*stress + WHtR *shoulder_factor * stress||Person), data = data)
tab_model(model2e3_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for strength factor #Table S51
model2e4_fat <- lmer(Rating ~ conception_risk * strength_factor*stress + WHtR * strength_factor * stress+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor*stress + WHtR * strength_factor * stress||Person), data = data)
tab_model(model2e4_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################
#with E/P rather than  conception risk

#also including between-women hormone effects in an exploratory manner

#for muscularity #Table S52
model2e5_fat <- lmer(Rating ~ E_P * Muscularity*stress + E_P_mean * Muscularity*stress + WHtR *Muscularity * stress + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity*stress + WHtR *Muscularity * stress||Person), data = data)
tab_model(model2e5_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S53
model2e6_fat <- lmer(Rating ~ E_P * dominance*stress + E_P_mean* dominance*stress + WHtR *dominance * stress+ ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance*stress + WHtR *dominance * stress||Person), data = data)
tab_model(model2e6_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1 #Table S54
model2e7_fat <- lmer(Rating ~ E_P * shoulder_factor*stress + E_P_mean* shoulder_factor*stress + WHtR *shoulder_factor * stress + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor*stress + WHtR *shoulder_factor * stress||Person), data = data)
tab_model(model2e7_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2 #Table S55
model2e8_fat <- lmer(Rating ~ E_P * strength_factor*stress + E_P_mean*strength_factor*stress + WHtR *strength_factor * stress + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor*stress + WHtR *strength_factor * stress||Person), data = data)
tab_model(model2e8_fat, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
```


```{r estradiol progesterone}
#All models with estradiol and progesterone separately rather than E/P
#also including between-women hormone effects in an exploratory manner

#for muscularity #Table S56
model2ep1 <- lmer(Rating ~ estradiol * Muscularity + estradiol_mean * Muscularity + progesterone * Muscularity + progesterone_mean * Muscularity + ( 1 | Person) + (1 | MaleID) + (1 + estradiol * Muscularity + progesterone * Muscularity||Person), data = data)
tab_model(model2ep1, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S56
model2ep2 <- lmer(Rating ~ estradiol * dominance + estradiol_mean* dominance + progesterone * dominance + progesterone_mean* dominance + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* dominance + progesterone * dominance||Person), data = data)
tab_model(model2ep2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1 #Table S57
model2ep3 <- lmer(Rating ~ estradiol * shoulder_factor + estradiol_mean* shoulder_factor + progesterone * shoulder_factor + progesterone_mean* shoulder_factor + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* shoulder_factor + progesterone * shoulder_factor||Person), data = data)
tab_model(model2ep3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2 #Table S57
model2ep4 <- lmer(Rating ~ estradiol * strength_factor + estradiol_mean*strength_factor + progesterone * strength_factor + progesterone_mean*strength_factor + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* strength_factor + progesterone * strength_factor||Person), data = data)
tab_model(model2ep4, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################
#three-way interaction with relationship status

#also including between-women hormone effects in an exploratory manner

#for muscularity #Table S58
model2ep5 <- lmer(Rating ~ estradiol * Muscularity*relationship_status + estradiol_mean * Muscularity*relationship_status + progesterone * Muscularity*relationship_status + progesterone_mean * Muscularity*relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + estradiol * Muscularity*relationship_status + progesterone * Muscularity*relationship_status ||Person), data = data)
tab_model(model2ep5, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S59
model2ep6 <- lmer(Rating ~ estradiol * dominance*relationship_status + estradiol_mean* dominance*relationship_status + progesterone * dominance*relationship_status + progesterone_mean* dominance*relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* dominance*relationship_status + progesterone * dominance*relationship_status||Person), data = data)
tab_model(model2ep6, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1 #Table S60
model2ep7 <- lmer(Rating ~ estradiol * shoulder_factor*relationship_status + estradiol_mean* shoulder_factor*relationship_status + progesterone * shoulder_factor*relationship_status + progesterone_mean* shoulder_factor*relationship_status  + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* shoulder_factor* relationship_status + progesterone * shoulder_factor*relationship_status||Person), data = data)
tab_model(model2ep7, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2 #Table S61
model2ep8 <- lmer(Rating ~ estradiol * strength_factor*relationship_status + estradiol_mean*strength_factor*relationship_status + progesterone * strength_factor*relationship_status + progesterone_mean*strength_factor*relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* strength_factor*relationship_status + progesterone * strength_factor*relationship_status||Person), data = data)
tab_model(model2ep8, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

######################################################################################
#three-way interaction with self-reported stress

#for muscularity #Table S62
model2ep5 <- lmer(Rating ~ estradiol * Muscularity*stress + estradiol_mean * Muscularity*stress + progesterone * Muscularity*stress + progesterone_mean * Muscularity*stress + ( 1 | Person) + (1 | MaleID) + (1 + estradiol * Muscularity*stress + progesterone * Muscularity*stress||Person), data = data)
tab_model(model2ep5, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S63
model2ep6 <- lmer(Rating ~ estradiol * dominance*stress + estradiol_mean* dominance*stress + progesterone * dominance*stress + progesterone_mean* dominance*stress + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* dominance*stress + progesterone * dominance*stress||Person), data = data)
tab_model(model2ep6, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1 #Table S64
model2ep7 <- lmer(Rating ~ estradiol * shoulder_factor*stress + estradiol_mean* shoulder_factor*stress + progesterone * shoulder_factor*stress + progesterone_mean* shoulder_factor*stress + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* shoulder_factor*stress + progesterone * shoulder_factor*stress||Person), data = data)
tab_model(model2ep7, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2 #Table S65
model2ep8 <- lmer(Rating ~ estradiol * strength_factor*stress + estradiol_mean*strength_factor*stress + progesterone * strength_factor*stress + progesterone_mean*strength_factor*stress + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* strength_factor*stress + progesterone * strength_factor*stress||Person), data = data)
tab_model(model2ep8, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

############################################################################################################
#controlling for body fat mass (WHtR)
############################################################################################################

#for muscularity #Table S66
model2ep9 <- lmer(Rating ~ estradiol * Muscularity + estradiol_mean * Muscularity + progesterone * Muscularity + progesterone_mean * Muscularity + WHtR *Muscularity + ( 1 | Person) + (1 | MaleID) + (1 + estradiol * Muscularity + progesterone * Muscularity + WHtR *Muscularity||Person), data = data)
tab_model(model2ep9, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S67
model2ep10 <- lmer(Rating ~ estradiol * dominance + estradiol_mean* dominance + progesterone * dominance + progesterone_mean* dominance + WHtR *dominance + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* dominance + progesterone * dominance + WHtR *dominance||Person), data = data)
tab_model(model2ep10, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1 #Table S68
model2ep11 <- lmer(Rating ~ estradiol * shoulder_factor + estradiol_mean* shoulder_factor + progesterone * shoulder_factor + progesterone_mean* shoulder_factor + WHtR *shoulder_factor + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* shoulder_factor + progesterone * shoulder_factor + WHtR *shoulder_factor||Person), data = data)
tab_model(model2ep11, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2 #Table S69
model2ep12 <- lmer(Rating ~ estradiol * strength_factor + estradiol_mean*strength_factor + progesterone * strength_factor + progesterone_mean*strength_factor + WHtR *strength_factor + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* strength_factor + progesterone * strength_factor + WHtR *strength_factor||Person), data = data)
tab_model(model2ep12, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################
#three-way interaction with relationship status

#also including between-women hormone effects in an exploratory manner

#for muscularity #Table S70
model2ep13 <- lmer(Rating ~ estradiol * Muscularity*relationship_status + estradiol_mean * Muscularity*relationship_status + progesterone * Muscularity*relationship_status + progesterone_mean * Muscularity*relationship_status + WHtR *Muscularity * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + estradiol * Muscularity*relationship_status + progesterone * Muscularity*relationship_status + WHtR *Muscularity*relationship_status ||Person), data = data)
tab_model(model2ep13, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S71
model2ep14 <- lmer(Rating ~ estradiol * dominance*relationship_status + estradiol_mean* dominance*relationship_status + progesterone * dominance*relationship_status + progesterone_mean* dominance*relationship_status + + WHtR * dominance * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* dominance*relationship_status + progesterone * dominance*relationship_status + WHtR *dominance * relationship_status||Person), data = data)
tab_model(model2ep14, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1 #Table S72
model2ep15 <- lmer(Rating ~ estradiol * shoulder_factor*relationship_status + estradiol_mean* shoulder_factor*relationship_status + progesterone * shoulder_factor*relationship_status + progesterone_mean* shoulder_factor*relationship_status  + WHtR * shoulder_factor * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* shoulder_factor* relationship_status + progesterone * shoulder_factor*relationship_status + WHtR *shoulder_factor * relationship_status ||Person), data = data)
tab_model(model2ep15, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2 #Table S73
model2ep16 <- lmer(Rating ~ estradiol * strength_factor*relationship_status + estradiol_mean*strength_factor*relationship_status + progesterone * strength_factor*relationship_status + progesterone_mean*strength_factor*relationship_status + WHtR * strength_factor * relationship_status+ ( 1 | Person) + (1 | MaleID) + (1 + estradiol* strength_factor*relationship_status + progesterone * strength_factor*relationship_status + WHtR *strength_factor * relationship_status ||Person), data = data)
tab_model(model2ep16, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

######################################################################################
#three-way interaction with self-reported stress

#for muscularity #Table S74
model2ep17 <- lmer(Rating ~ estradiol * Muscularity*stress + estradiol_mean * Muscularity*stress + progesterone * Muscularity*stress + progesterone_mean * Muscularity*stress + WHtR *Muscularity * stress+ ( 1 | Person) + (1 | MaleID) + (1 + estradiol * Muscularity*stress + progesterone * Muscularity*stress + WHtR *Muscularity * stress||Person), data = data)
tab_model(model2ep17, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance #Table S75
model2ep18 <- lmer(Rating ~ estradiol * dominance*stress + estradiol_mean* dominance*stress + progesterone * dominance*stress + progesterone_mean* dominance*stress + WHtR * dominance * stress+ ( 1 | Person) + (1 | MaleID) + (1 + estradiol* dominance*stress + progesterone * dominance*stress + WHtR *dominance * stress||Person), data = data)
tab_model(model2ep18, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1 #Table S76
model2ep19 <- lmer(Rating ~ estradiol * shoulder_factor*stress + estradiol_mean* shoulder_factor*stress + progesterone * shoulder_factor*stress + progesterone_mean* shoulder_factor*stress + WHtR * shoulder_factor * stress+ ( 1 | Person) + (1 | MaleID) + (1 + estradiol* shoulder_factor*stress + progesterone * shoulder_factor*stress + WHtR *shoulder_factor * stress||Person), data = data)
tab_model(model2ep19, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2 #Table S77
model2ep20 <- lmer(Rating ~ estradiol * strength_factor*stress + estradiol_mean*strength_factor*stress + progesterone * strength_factor*stress + progesterone_mean*strength_factor*stress + WHtR * strength_factor * stress + ( 1 | Person) + (1 | MaleID) + (1 + estradiol* strength_factor*stress + progesterone * strength_factor*stress + WHtR *strength_factor * stress||Person), data = data)
tab_model(model2ep20, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
```


```{r}
#Repeat main models from Hypotheses 2c, 2f with masculine indicators separately
#names(data)

###with conception risk (2c)
#for strength #Table S19
model2c3 <- lmer(Rating ~ conception_risk * strength+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk * strength ||Person), data = data)
tab_model(model2c3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for height #Table S19
model2c4 <- lmer(Rating ~ conception_risk * height + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk * height ||Person), data = data)
tab_model(model2c4, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for upperarm circumference #Table S19
model2c5 <- lmer(Rating ~ conception_risk * upperarmgirth_mean_leftright + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk * upperarmgirth_mean_leftright ||Person), data = data)
tab_model(model2c5, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for SHR #Table S19
model2c6 <- lmer(Rating ~ conception_risk * SHR + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk * SHR ||Person), data = data)
tab_model(model2c6, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for SCR #Table S20
model2c7 <- lmer(Rating ~ conception_risk * SCR + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk * SCR ||Person), data = data)
tab_model(model2c7, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for relative torso volumne #Table S20
model2c8 <- lmer(Rating ~ conception_risk * rel_torso_vol + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk * rel_torso_vol ||Person), data = data)
tab_model(model2c8, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for testosterone levels #Table S20
model2c9 <- lmer(Rating ~ conception_risk * testosterone_men + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk * testosterone_men ||Person), data = data)
tab_model(model2c9, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)


###with E/P (2f)
#for strength #Table S21
model2f5 <- lmer(Rating ~ E_P * strength + E_P_mean * strength + ( 1 | Person) + (1 | MaleID) + (1 + E_P * strength ||Person), data = data)
tab_model(model2f5, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for height #Table S21
model2f6 <- lmer(Rating ~ E_P * height + E_P_mean * height + ( 1 | Person) + (1 | MaleID) + (1 + E_P * height ||Person), data = data)
tab_model(model2f6, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for upperarm circumference #Table S21
model2f7 <- lmer(Rating ~ E_P * upperarmgirth_mean_leftright + E_P_mean * upperarmgirth_mean_leftright + ( 1 | Person) + (1 | MaleID) + (1 + E_P * upperarmgirth_mean_leftright ||Person), data = data)
tab_model(model2f7, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for SHR #Table S22
model2f8 <- lmer(Rating ~ E_P * SHR + E_P_mean * SHR + ( 1 | Person) + (1 | MaleID) + (1 + E_P * SHR ||Person), data = data)
tab_model(model2f8, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for SCR #Table S22
model2f9 <- lmer(Rating ~ E_P * SCR + E_P_mean * SCR + ( 1 | Person) + (1 | MaleID) + (1 + E_P * SCR ||Person), data = data)
tab_model(model2f9, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for relative torso volumne #Table S22
model2f10 <- lmer(Rating ~ E_P * rel_torso_vol + E_P_mean * rel_torso_vol + ( 1 | Person) + (1 | MaleID) + (1 + E_P * rel_torso_vol ||Person), data = data)
tab_model(model2f10, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for testosterone levels #Table S23
model2f11 <- lmer(Rating ~ E_P * testosterone_men + E_P_mean * testosterone_men + ( 1 | Person) + (1 | MaleID) + (1 + E_P * testosterone_men ||Person), data = data)
tab_model(model2f11, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
```
```{r Cycle shifts in attraction controlling for session}

###Controlling main analyses for session

#Hypothesis 1a
s_model1a <- lmer(Rating ~ conception_risk + Session + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk ||Person), data = data)
tab_model(s_model1a, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#with E_P ratio, Hypothesis 1b
s_model1b <- lmer(Rating ~ E_P + Session + ( 1 | Person) + (1 | MaleID) + (1 + E_P||Person), data = data)
tab_model(s_model1b, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#moderated by relationship status, Hypothesis 1c
s_model1c<- lmer(Rating ~ conception_risk * relationship_status + Session + (1 |Person) + (1 | MaleID) + (1+ conception_risk*relationship_status||Person),  data = data)
tab_model(s_model1c, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#moderated by relationship status, but with E_P ratio, Hypothesis 1d
s_model1c2<- lmer(Rating ~ E_P * relationship_status + Session + (1 |Person) + (1 | MaleID) + (1+ E_P*relationship_status||Person),  data = data)
tab_model(s_model1c2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#moderated by self-reported stress, Hypothesis 1d
s_model1d<- lmer(Rating ~ conception_risk * stress + Session + (1 |Person) + (1 | MaleID) + (1+ conception_risk*stress||Person),  data = data)
tab_model(s_model1d, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#moderated by self-reported stress, but with E_P ratio, Hypothesis 1d
s_model1d2<- lmer(Rating ~ E_P * stress + Session + (1 |Person) + (1 | MaleID) + (1+ E_P*stress||Person),  data = data)
tab_model(s_model1d2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#shifts in mate attraction mediated by sexual desire? H1e

#Premises H1e:
#effect of mediator on outcome
s_model_p1_H1e1 <- lmer(Rating ~ roney_desire + Session + ( 1 | Person) + (1 | MaleID) + (1 + roney_desire ||Person), data = data)
tab_model(s_model_p1_H1e1, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#effect of predictor on mediator
s_model_p2_H1e1 <- lmer(roney_desire ~ conception_risk + Session + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk||Person), data = data)
tab_model(s_model_p2_H1e1, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Test H1e:
s_modelH1e1<- lmer(Rating ~ conception_risk +roney_desire + Session + (1 | Person) + (1 | MaleID) + (1 + conception_risk + roney_desire || Person), data = data)
tab_model(s_modelH1e1, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for E/P rather than conception risk
#premise: Effect of predictor on mediator
s_P2_modelH1e2<- lmer(roney_desire ~ E_P + Session +(1 | Person) + (1 | MaleID) + (1+ E_P||Person), data = data)
tab_model(s_P2_modelH1e2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#testing Hypothesis 1e for E/P
s_modelH1e2<- lmer(Rating ~ E_P + roney_desire + Session + (1 | Person) + (1 | MaleID) + (1 + E_P + roney_desire||Person), data = data)
tab_model(s_modelH1e2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 1f: Attraction shift (of conception risk) mediated by E/P?

#Premise H1f:
s_P_modelH1f<- lmer(E_P ~ conception_risk + Session + (1 | Person) + (1 | MaleID) + (1+conception_risk ||Person), data = data)
tab_model(s_P_modelH1f, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Test H1f:
s_modelH1f<- lmer(Rating ~ conception_risk + E_P + Session + (1 | Person) + (1 | MaleID) + (1+conception_risk+ E_P||Person), data = data)
tab_model(s_modelH1f,show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
```



```{r controlling for session 2}
#main analyses for preference shifts controlling for session

#Hypothesis 2a
s_model2g <- lmer(Rating ~ conception_risk * Muscularity + Session + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity||Person), data = data)
tab_model(s_model2g, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2b: for dominance
s_model2b <- lmer(Rating ~ conception_risk * dominance + Session + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance||Person), data = data)
tab_model(s_model2b, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2c: for factor 1
s_model2c <- lmer(Rating ~ conception_risk * shoulder_factor + Session + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor||Person), data = data)
tab_model(s_model2c, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2c: for factor 2
s_model2c2 <- lmer(Rating ~ conception_risk * strength_factor + Session + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor||Person), data = data)
tab_model(s_model2c2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#######################################################################################################
#with E/P rather than conception risk, Hypothesis 2f, Table 4
#also including between-women hormone effects in an exploratory manner

#for muscularity
s_model2f1 <- lmer(Rating ~ E_P * Muscularity + E_P_mean * Muscularity + Session + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity ||Person), data = data)
tab_model(s_model2f1, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
s_model2f2 <- lmer(Rating ~ E_P * dominance + E_P_mean* dominance + Session + ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance||Person), data = data)
tab_model(s_model2f2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1
s_model2f3 <- lmer(Rating ~ E_P * shoulder_factor + E_P_mean* shoulder_factor + Session + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor||Person), data = data)
tab_model(s_model2f3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2
s_model2f4 <- lmer(Rating ~ E_P * strength_factor + E_P_mean*strength_factor + Session+ ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor||Person), data = data)
tab_model(s_model2f4, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################

#3-way Interactions with relationship status: Hypothesis 2d
#for muscularity
s_model2d <- lmer(Rating ~ conception_risk * Muscularity * relationship_status + Session +( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity*relationship_status||Person), data = data)
tab_model(s_model2d, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
s_model2d2 <- lmer(Rating ~ conception_risk * dominance*relationship_status + Session+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance*relationship_status||Person), data = data)
tab_model(s_model2d2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for shoulder factor
s_model2d3<- lmer(Rating ~ conception_risk * shoulder_factor*relationship_status + Session + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor*relationship_status||Person), data = data)
tab_model(s_model2d3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for strength factor
s_model2d4 <- lmer(Rating ~ conception_risk * strength_factor*relationship_status + Session + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor*relationship_status||Person), data = data)
tab_model(s_model2d4, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################
#with E/P rather than  conception risk

#also including between-women hormone effects in an exploratory manner

#for muscularity
s_model2d5 <- lmer(Rating ~ E_P * Muscularity*relationship_status + E_P_mean * Muscularity*relationship_status + Session + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity*relationship_status||Person), data = data)
tab_model(s_model2d5, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
s_model2d6<- lmer(Rating ~ E_P * dominance*relationship_status + E_P_mean* dominance*relationship_status + Session + ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance*relationship_status||Person), data = data)
tab_model(s_model2d6, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1
s_model2d7 <- lmer(Rating ~ E_P * shoulder_factor*relationship_status + E_P_mean* shoulder_factor*relationship_status + Session + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor* relationship_status||Person), data = data)
tab_model(s_model2d7, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2
s_model2d8 <- lmer(Rating ~ E_P * strength_factor*relationship_status + E_P_mean*strength_factor*relationship_status + Session + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor*relationship_status||Person), data = data)
tab_model(s_model2d8, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#3-way Interactions with self-reported stress: Hypothesis 2e
#for muscularity
s_model2e <- lmer(Rating ~ conception_risk * Muscularity * stress + Session+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity*stress||Person), data = data)
tab_model(s_model2e, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
s_model2e2 <- lmer(Rating ~ conception_risk * dominance*stress + Session+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance*stress||Person), data = data)
tab_model(s_model2e2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for shoulder factor
s_model2e3<- lmer(Rating ~ conception_risk * shoulder_factor*stress + Session + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor*stress||Person), data = data)
tab_model(s_model2e3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for strength factor
s_model2e4 <- lmer(Rating ~ conception_risk * strength_factor*stress + Session+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor*stress||Person), data = data)
tab_model(s_model2e4, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################
#with E/P rather than  conception risk

#also including between-women hormone effects in an exploratory manner

#for muscularity
s_model2e5 <- lmer(Rating ~ E_P * Muscularity*stress + E_P_mean * Muscularity*stress + Session + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity*stress ||Person), data = data)
tab_model(s_model2e5, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
s_model2e6 <- lmer(Rating ~ E_P * dominance*stress + E_P_mean* dominance*stress + Session+ ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance*stress||Person), data = data)
tab_model(s_model2e6, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1
s_model2e7 <- lmer(Rating ~ E_P * shoulder_factor*stress + E_P_mean* shoulder_factor*stress + Session + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor*stress||Person), data = data)
tab_model(s_model2e7, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2
s_model2e8 <- lmer(Rating ~ E_P * strength_factor*stress + E_P_mean*strength_factor*stress + Session + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor*stress||Person), data = data)
tab_model(s_model2e8, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
```



```{r WHR body fat mass}
#controlling for body fat mass (with WHR rather than WHtR), Hypothesis 2g

#Hypothesis 2a controlling for WHR
model2g_fat2 <- lmer(Rating ~ conception_risk * Muscularity + WHR * Muscularity+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity + WHR * Muscularity||Person), data = data)
tab_model(model2g_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2b: for dominance
model2b_fat2 <- lmer(Rating ~ conception_risk * dominance + WHR *dominance + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance + WHR *dominance||Person), data = data)
tab_model(model2b_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2c: for factor 1
model2c_fat2 <- lmer(Rating ~ conception_risk * shoulder_factor + WHR *shoulder_factor + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor + WHR *shoulder_factor||Person), data = data)
tab_model(model2c_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2c: for factor 2
model2c2_fat2 <- lmer(Rating ~ conception_risk * strength_factor + WHR *strength_factor + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor + WHR *strength_factor||Person), data = data)
tab_model(model2c2_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#######################################################################################################
#with E/P rather than conception risk, Hypothesis 2f, Table 4
#also including between-women hormone effects in an exploratory manner

#for muscularity
model2f1_fat2 <- lmer(Rating ~ E_P * Muscularity + E_P_mean * Muscularity + WHR *Muscularity + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity + WHR *Muscularity ||Person), data = data)
tab_model(model2f1_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
model2f2_fat2 <- lmer(Rating ~ E_P * dominance + E_P_mean* dominance + WHR *dominance + ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance + WHR *dominance||Person), data = data)
tab_model(model2f2_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1
model2f3_fat2 <- lmer(Rating ~ E_P * shoulder_factor + E_P_mean* shoulder_factor + WHR *shoulder_factor + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor+ WHR *shoulder_factor||Person), data = data)
tab_model(model2f3_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2
model2f4_fat2 <- lmer(Rating ~ E_P * strength_factor + E_P_mean*strength_factor + WHR *strength_factor + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor + WHR *strength_factor||Person), data = data)
tab_model(model2f4_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################

#3-way Interactions with relationship status: Hypothesis 2d
#for muscularity
model2d_fat2 <- lmer(Rating ~ conception_risk * Muscularity * relationship_status + WHR *Muscularity* relationship_status+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity*relationship_status + WHR *Muscularity*relationship_status||Person), data = data)
tab_model(model2d_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
model2d2_fat2 <- lmer(Rating ~ conception_risk * dominance*relationship_status + WHR *dominance*relationship_status+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance*relationship_status + WHR *dominance *relationship_status||Person), data = data)
tab_model(model2d2_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for shoulder factor
model2d3_fat2 <- lmer(Rating ~ conception_risk * shoulder_factor*relationship_status + WHR *shoulder_factor * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor*relationship_status + WHR *shoulder_factor* relationship_status||Person), data = data)
tab_model(model2d3_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for strength factor
model2d4_fat2 <- lmer(Rating ~ conception_risk * strength_factor*relationship_status + WHR *strength_factor * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor*relationship_status + WHR *strength_factor * relationship_status||Person), data = data)
tab_model(model2d4_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################
#with E/P rather than  conception risk

#also including between-women hormone effects in an exploratory manner

#for muscularity
model2d5_fat2 <- lmer(Rating ~ E_P * Muscularity*relationship_status + E_P_mean * Muscularity*relationship_status + WHR *Muscularity * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity*relationship_status + WHR *Muscularity * relationship_status||Person), data = data)
tab_model(model2d5_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
model2d6_fat2 <- lmer(Rating ~ E_P * dominance*relationship_status + E_P_mean* dominance*relationship_status + WHR * dominance * relationship_status+ ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance*relationship_status + WHR *dominance * relationship_status||Person), data = data)
tab_model(model2d6_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1
model2d7_fat2 <- lmer(Rating ~ E_P * shoulder_factor*relationship_status + E_P_mean* shoulder_factor*relationship_status + WHR *shoulder_factor * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor* relationship_status + WHR *shoulder_factor* relationship_status||Person), data = data)
tab_model(model2d7_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2
model2d8_fat2 <- lmer(Rating ~ E_P * strength_factor*relationship_status + E_P_mean*strength_factor*relationship_status + WHR * strength_factor * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor*relationship_status + WHR *strength_factor * relationship_status||Person), data = data)
tab_model(model2d8_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#3-way Interactions with self-reported stress: Hypothesis 2e
#for muscularity
model2e_fat2 <- lmer(Rating ~ conception_risk * Muscularity * stress + WHR * Muscularity * stress+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity*stress + WHR *Muscularity * stress||Person), data = data)
tab_model(model2e_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
model2e2_fat2 <- lmer(Rating ~ conception_risk * dominance*stress + WHR * dominance * stress+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance*stress + WHR *dominance * stress||Person), data = data)
tab_model(model2e2_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for shoulder factor
model2e3_fat2 <- lmer(Rating ~ conception_risk * shoulder_factor*stress + WHR * shoulder_factor * stress + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor*stress + WHR *shoulder_factor * stress||Person), data = data)
tab_model(model2e3_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for strength factor
model2e4_fat2 <- lmer(Rating ~ conception_risk * strength_factor*stress + WHR * strength_factor * stress+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor*stress + WHR * strength_factor * stress||Person), data = data)
tab_model(model2e4_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################
#with E/P rather than  conception risk

#also including between-women hormone effects in an exploratory manner

#for muscularity
model2e5_fat2 <- lmer(Rating ~ E_P * Muscularity*stress + E_P_mean * Muscularity*stress + WHR *Muscularity * stress + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity*stress + WHR *Muscularity * stress||Person), data = data)
tab_model(model2e5_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
model2e6_fat2 <- lmer(Rating ~ E_P * dominance*stress + E_P_mean* dominance*stress + WHR *dominance * stress+ ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance*stress + WHR *dominance * stress||Person), data = data)
tab_model(model2e6_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1
model2e7_fat2 <- lmer(Rating ~ E_P * shoulder_factor*stress + E_P_mean* shoulder_factor*stress + WHR *shoulder_factor * stress + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor*stress + WHR *shoulder_factor * stress||Person), data = data)
tab_model(model2e7_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2
model2e8_fat2 <- lmer(Rating ~ E_P * strength_factor*stress + E_P_mean*strength_factor*stress + WHR *strength_factor * stress + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor*stress + WHR *strength_factor * stress||Person), data = data)
tab_model(model2e8_fat2, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)
```



```{r BMI body fat mass}
#controlling for body fat mass (with BMI rather than WHtR), Hypothesis 2g

#Hypothesis 2a controlling for BMI
model2g_fat3 <- lmer(Rating ~ conception_risk * Muscularity + BMI * Muscularity+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity + BMI * Muscularity||Person), data = data)
tab_model(model2g_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2b: for dominance
model2b_fat3 <- lmer(Rating ~ conception_risk * dominance + BMI *dominance + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance + BMI *dominance||Person), data = data)
tab_model(model2b_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2c: for factor 1
model2c_fat3 <- lmer(Rating ~ conception_risk * shoulder_factor + BMI *shoulder_factor + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor + BMI *shoulder_factor||Person), data = data)
tab_model(model2c_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#Hypothesis 2c: for factor 2
model2c2_fat3 <- lmer(Rating ~ conception_risk * strength_factor + BMI *strength_factor + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor + BMI *strength_factor||Person), data = data)
tab_model(model2c2_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#######################################################################################################
#with E/P rather than conception risk, Hypothesis 2f, Table 4
#also including between-women hormone effects in an exploratory manner

#for muscularity
model2f1_fat3 <- lmer(Rating ~ E_P * Muscularity + E_P_mean * Muscularity + BMI *Muscularity + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity + BMI *Muscularity ||Person), data = data)
tab_model(model2f1_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
model2f2_fat3 <- lmer(Rating ~ E_P * dominance + E_P_mean* dominance + BMI *dominance + ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance + BMI *dominance||Person), data = data)
tab_model(model2f2_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1
model2f3_fat3 <- lmer(Rating ~ E_P * shoulder_factor + E_P_mean* shoulder_factor + BMI *shoulder_factor + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor+ BMI *shoulder_factor||Person), data = data)
tab_model(model2f3_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2
model2f4_fat3 <- lmer(Rating ~ E_P * strength_factor + E_P_mean*strength_factor + BMI *strength_factor + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor + BMI *strength_factor||Person), data = data)
tab_model(model2f4_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################

#3-way Interactions with relationship status: Hypothesis 2d
#for muscularity
model2d_fat3 <- lmer(Rating ~ conception_risk * Muscularity * relationship_status + BMI *Muscularity* relationship_status+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity*relationship_status + BMI *Muscularity*relationship_status||Person), data = data)
tab_model(model2d_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
model2d2_fat3 <- lmer(Rating ~ conception_risk * dominance*relationship_status + BMI *dominance*relationship_status+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance*relationship_status + BMI *dominance *relationship_status||Person), data = data)
tab_model(model2d2_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for shoulder factor
model2d3_fat3 <- lmer(Rating ~ conception_risk * shoulder_factor*relationship_status + BMI *shoulder_factor * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor*relationship_status + BMI *shoulder_factor* relationship_status||Person), data = data)
tab_model(model2d3_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for strength factor
model2d4_fat3 <- lmer(Rating ~ conception_risk * strength_factor*relationship_status + BMI *strength_factor * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor*relationship_status + BMI *strength_factor * relationship_status||Person), data = data)
tab_model(model2d4_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################
#with E/P rather than  conception risk

#also including between-women hormone effects in an exploratory manner

#for muscularity
model2d5_fat3 <- lmer(Rating ~ E_P * Muscularity*relationship_status + E_P_mean * Muscularity*relationship_status + BMI *Muscularity * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity*relationship_status + BMI *Muscularity * relationship_status||Person), data = data)
tab_model(model2d5_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
model2d6_fat3 <- lmer(Rating ~ E_P * dominance*relationship_status + E_P_mean* dominance*relationship_status + BMI * dominance * relationship_status+ ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance*relationship_status + BMI *dominance * relationship_status||Person), data = data)
tab_model(model2d6_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1
model2d7_fat3 <- lmer(Rating ~ E_P * shoulder_factor*relationship_status + E_P_mean* shoulder_factor*relationship_status + BMI *shoulder_factor * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor* relationship_status + BMI *shoulder_factor* relationship_status||Person), data = data)
tab_model(model2d7_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2
model2d8_fat3 <- lmer(Rating ~ E_P * strength_factor*relationship_status + E_P_mean*strength_factor*relationship_status + BMI * strength_factor * relationship_status + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor*relationship_status + BMI *strength_factor * relationship_status||Person), data = data)
tab_model(model2d8_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#3-way Interactions with self-reported stress: Hypothesis 2e
#for muscularity
model2e_fat3 <- lmer(Rating ~ conception_risk * Muscularity * stress + BMI * Muscularity * stress+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* Muscularity*stress + BMI *Muscularity * stress||Person), data = data)
tab_model(model2e_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
model2e2_fat3 <- lmer(Rating ~ conception_risk * dominance*stress + BMI * dominance * stress+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* dominance*stress + BMI *dominance * stress||Person), data = data)
tab_model(model2e2_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for shoulder factor
model2e3_fat3 <- lmer(Rating ~ conception_risk * shoulder_factor*stress + BMI * shoulder_factor * stress + ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* shoulder_factor*stress + BMI *shoulder_factor * stress||Person), data = data)
tab_model(model2e3_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for strength factor
model2e4_fat3 <- lmer(Rating ~ conception_risk * strength_factor*stress + BMI * strength_factor * stress+ ( 1 | Person) + (1 | MaleID) + (1 + conception_risk* strength_factor*stress + BMI * strength_factor * stress||Person), data = data)
tab_model(model2e4_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

########################################################################################################
#with E/P rather than  conception risk

#also including between-women hormone effects in an exploratory manner

#for muscularity
model2e5_fat3 <- lmer(Rating ~ E_P * Muscularity*stress + E_P_mean * Muscularity*stress + BMI *Muscularity * stress + ( 1 | Person) + (1 | MaleID) + (1 + E_P * Muscularity*stress + BMI *Muscularity * stress||Person), data = data)
tab_model(model2e5_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for dominance
model2e6_fat3 <- lmer(Rating ~ E_P * dominance*stress + E_P_mean* dominance*stress + BMI *dominance * stress+ ( 1 | Person) + (1 | MaleID) + (1 + E_P* dominance*stress + BMI *dominance * stress||Person), data = data)
tab_model(model2e6_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 1
model2e7_fat3 <- lmer(Rating ~ E_P * shoulder_factor*stress + E_P_mean* shoulder_factor*stress + BMI *shoulder_factor * stress + ( 1 | Person) + (1 | MaleID) + (1 + E_P* shoulder_factor*stress + BMI *shoulder_factor * stress||Person), data = data)
tab_model(model2e7_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

#for factor 2
model2e8_fat3 <- lmer(Rating ~ E_P * strength_factor*stress + E_P_mean*strength_factor*stress + BMI *strength_factor * stress + ( 1 | Person) + (1 | MaleID) + (1 + E_P* strength_factor*stress + BMI *strength_factor * stress||Person), data = data)
tab_model(model2e8_fat3, show.se = TRUE, show.stat = TRUE, show.re.var = FALSE)

```

